%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS

\documentclass{template} % Use the custom resume.cls style

\usepackage[left=0.7in,top=0.6in,right=0.7in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Akhil Goel}
%\address{7700 Falstaff Rd, McLean, VA 22102}
\address{https://github.com/agaction}
\address{(571) 353-9527 \\ akhil.goel@gatech.edu} % Your phone number and email

%%% Fall 2020 %%%

\begin{document}

% EDUCATION SECTION

\begin{rSection}{Education}

{\bf Georgia Institute of Technology, Atlanta, GA} \hfill {\em Aug 2018 - May 2022 (Expected)}
\\ Bachelors of Science in Mathematics \& Computer Science \hfill  GPA: 3.84/4.0 \medskip
\\ {\bf Thomas Jefferson HS for Science \& Technology} \hfill {\em July 2014 - June 2018}
\end{rSection}

% WORK EXPERIENCE

\begin{rSection}{Work Experience}

\begin{rSubsection}{Facebook AI Applied Research}{May 2021 - August 2021}{Softare Engineering Intern}{Menlo Park, CA}
\item Implemented model interpretability algorithms for Captum, an open-source PyTorch package.
\item Designed and developed a library for influential instance methods for machine learning models.
\item Created tutorials and applied algorithms to Facebook AI Multimodal models for platform integrity. 
\end{rSubsection}

\begin{rSubsection}{Varian Medical Systems}{May 2020 - August 2020}{Softare Engineering Intern}{Atlanta, GA}
\item Built automized data preprocessing pipeline for developing local deep learning segmentation models,
\item Developed deep volumetric models for organ segmentation within Varian's oncology PACS: Velocity.
\item Presented project \& pitched call-to-action to panel of Varian executives, received a top score.
\end{rSubsection}

\begin{rSubsection}{MIT Lincoln Laboratory}{June 2019 - August 2020}{Summer Research Intern \& Student Technical Researcher}{Lexington, MA}
\item Used Monte-Carlo simulations to develop a time-gating algorithm for a novel imaging technique.
\item Poster presentation at SPIE Photonics West, San Francisco, February 2020. "Towards Automatic Time-Gating for Time-Domain Diffuse Correlation Spectroscopy." Paper available at bit.ly/AGpaper1.
\item Implemented convolutional neural network architectures for nuclei segmentation and quantification of neurodegenerative disease biomarkers.
\item$1^{\text{st}}$ Place Team and Best Poster in Intern Innovative Idea Challenge for proposal on automatic American Sign Language translation. Received funding for continued project development.
\end{rSubsection}

\begin{rSubsection}{GoVivace Inc.}{July 2018 - Aug 2018}{Research Intern}{McLean, VA}
\item Researched on using deep learning to enhance speech recognition accuracy.
\item Leveraged Kaldi toolkit to work on developing improved signal-to-noise ratio estimates, allowing for a better balance between the acoustic model and language model.
\end{rSubsection}

\begin{rSubsection}{George Mason University}{July 2017 - Aug 2017}{Intern - Aspiring Scientists Summer Internship Program}{Fairfax, VA}
\item Researched under Dr. Giorgio Ascoli on dendritic arborization by creating 3D reconstructions of neurons.
\item Presented results to peers, work will be added to the NeuroMorpho database.
\end{rSubsection}

\begin{rSubsection}{eKare Inc.}{July 2016 - Aug 2016}{Intern}{Fairfax, VA}
\item Worked on a product for noninvasive wound measurement with novel iPad-based 3D imaging technology.
\end{rSubsection}

\end{rSection}

% Projects And Seminars
\newpage

\begin{rSection}{Projects}
{\bf 3D Texture Generation at Georgia Tech Hays Lab} \hfill {\em August 2020 - Current} \smallskip
\\Research on using Generative Adversarial Nets and Neural Rendering to produce textured 3D images. \vspace{3mm} \\
{\bf American Sign Language Translation at MIT Lincoln Laboratory} \hfill {\em June 2019 - January 2020} \smallskip
\\Developed project proposal for automatic American Sign Language translation through deep learning with a team of six other interns. Continued research development is funded by MIT Lincoln Laboratory  \vspace{3mm} \\
{\bf Autonomous Robot Navigation at Georgia Tech IVALab} \hfill {\em Jan 2019 - May 2020} \smallskip
\\Applying reinforcement learning algorithms to improve traditional local planning methods in robotics. \vspace{3mm} \\
{\bf Coin Detection with OpenCV} \hfill {\em Nov 2017 - Feb 2018} \smallskip
\\Self-wrote fundamental computer vision algorithms such as
Gaussian blur, Canny Edge Detection, and Hough transform. Utilized OpenCV Library to identify different coins in a picture. \vspace{3mm} \\
{\bf Research on the Neuroscience of Long-Term Memory} \hfill {\em Sep 2017 - June 2018} \smallskip
\\Applied electrophysiology, self-written data analysis algorithms, and other interdisciplinary lab techniques to study the effect of a drug (zeta inhibitory peptide) on the learning of {\em Aplysia} (sea slugs).
\end{rSection}

%TECHNICAL STRENGTHS

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & Python, C/C++, Java, Bash, Matlab \\[2pt]
Software \& Tools & Git, Numpy, PyTorch, TensorFlow, LaTeX, Mathematica \\[2pt]
Concepts \& Coursework & Data Structures, Algorithms, AI,
Computer Vision, Machine Learning, \\& Deep Learning, Object-Oriented Programming, Prob/Stat Theory, \\& Applied Combinatorics, Vector Calculus, Advanced Linear Algebra
\end{tabular}

\end{rSection}

% Leadership & Extra Curricular
\begin{rSection}{Leadership \& Extracurricular} \itemsep -3pt \vspace{-3mm}
\item {\bf Treasurer for ``The Agency,''} the AI/ML club at Georgia Tech. Lead weekly beginner workshop series on theory and application of neural networks, preparing lectures, planning events.
\item {\bf Teaching free chess lessons} to roughly 20 elementary school kids at local library in summer 2017.
\item {\bf Camp Invention Leadership Intern} in summer 2016, learned leadership skills and worked with kids to promote effective teamwork.
\item {\bf Volunteered at my Elementary School Chess Club} in 2013-2014. Acted as the assistant of the instructor and helped manage more than a hundred students, chess sets, and logistics.
\end{rSection}

% Awards & Achievements

\begin{rSection}{Awards \& Achievements} \itemsep -3pt \vspace{-3mm}
\item {\bf Qualifier} for the 2018 and 2015 American Invitational Mathematics Examination (AIME)
\item {\bf Semifinalist (Top 500)} for the 2017 and 2016 USA Biology Olympiad (USABO)
\item {\bf First place school team} in 2018 National High School Chess Championships. First team in 2015-2018 VA State Championships.
\item {\bf National German Exam} Gold Award (2017),
Silver Award (2016, 2015)
\end{rSection}

\end{document}
