%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS

\documentclass{template} % Use the custom resume.cls style

\usepackage[left=0.7in,top=0.5in,right=0.7in,bottom=0.5in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Nagendra Goel}
%\address{7700 Falstaff Rd, McLean, VA 22102}
\address{https://linkedin.com/in/ngoel}
\address{(703)\:869\:-\:9463 \\ nagendra.goel@gmail.com} % Your phone number and email

\begin{document}

% EDUCATION SECTION

\begin{rSection}{Education}
\begin{rSubsection}{The Johns Hopkins University, Baltimore, MD}{1992 - 1997}{Doctor of Philosophy in Electrical Engineering}{}
\end{rSubsection}
\vspace{-0.2cm}
\begin{rSubsection}{Indian Institute of Technology, Kanpur, IN}{1985 - 1989}{Bachelor of Technology \& Electrical Engineering}{GPA: 3.9/4.0}
\end{rSubsection}
\vspace{-0.2cm}
\end{rSection}

% WORK EXPERIENCE

\begin{rSection}{Work Experience}

\begin{rSubsection}{GoVivace Inc.}{May 2009 - Present}{Founder, CEO}{McLean, VA}
\item Managed engineering team and provided technical leadership to deliver speech recognition, audio indexing, speaker identification, speaker verification, and NLU solutions as SAAS products for clients.
\item Built web solutions based on these core services. 3 patents were filed, 1 awarded.
\item Responsible for sales and marketing.
\end{rSubsection}

\begin{rSubsection}{Enabledoc LLC}{May 2009 - present}{Co-Founder}{McLean, VA}
\item Founded the company and implemented core technology functions. Set up and managed the technical team until self-sufficient.
\end{rSubsection}

\begin{rSubsection}{Net2Voice/Apptek}{June 2005 - May 2009}{Manager Speech Products}{McLean, VA}
\item Developed speech recognition for voicemail to email, television broadcast to text conversion, and a portable speech-to-speech translation system for Iraqi to English and Farsi to Arabic, and High Volume IVR applications.
\end{rSubsection}

\begin{rSubsection}{LSI, an Avago Technologies Company}{2001 - 2005}{Senior/Principal Engineer}{Gaithesburg, MD}
\item System-level modeling of a digital TV receiver for US digital television network. \item Team lead for ADSL2 firmware development. Member of the ZSP DSP firmware development team. 
\item Work resulted in 3 patents and some magazine publications.
\end{rSubsection}

\begin{rSubsection}{IBM T. J. Watson Research Center}{2000 - 2001}{Researcher}{Yorktown Heights, NY}
\item Developed and implemented new algorithms, to improve the performance of the current speech recognition systems. 
\item Received two patents and one publication.
\end{rSubsection}

\begin{rSubsection}{Entropic Inc., Telogy Networks}{1997 - 2000}{Senior Engineer}{Washington, DC}
\item Implemented voice compression, recognition, echo cancellation, and other signal processing algorithms on fixed point DSP platforms to improve the quality of an Entropic trainable speech synthesis system. 
\item Received two patents.
\end{rSubsection}

27 publications in various peer-reviewed Conferences and Journals. 
\end{rSection}
\vspace{-2mm}

%Projects

%\begin{rSection}{Research}
%{\bf Visually Grounded PointGoal Navigation at CVMLP Lab} \hfill {\em August 2021 - May 2022} \smallskip
%\\Research on visually-grounded navigation in dynamic environments. Advised by Prof. Dhruv Batra. \vspace{3mm} \\
%{\bf Autonomous Robot Navigation at Georgia Tech IVALab} \hfill {\em Jan 2019 - May 2020} \smallskip
%\\Applying reinforcement learning algorithms to improve traditional local planning methods in robotics.
%\end{rSection}

%TECHNICAL STRENGTHS

%\begin{rSection}{Technical Skills}

%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
%Programming Languages & Python, Java, C/C++, Bash \\[2pt]
%Software \& Tools & PyTorch, Tensorflow/Keras, Numpy, Git, Mercurial, LaTeX \\[2pt]
%Concepts \& Coursework & Probability Theory, Statistics, Combinatorics, Numerical Analysis, AI, \\&  Stochastic Processes, Data %Structures, Algorithms, Computer Vision, \\& Deep Learning, Vector Calculus, Linear Algebra, Comp.\:Architecture, \\& Convex %Optimization, High Performance Parallel Computing
%\end{tabular}

%\end{rSection}

% Leadership & Extra Curricular

%\begin{rSection}{Leadership \& Extracurricular} \itemsep -3pt \vspace{-3mm}
%\item {\bf External Operations - The Agency:} President for AI/ML research club at Georgia Tech.
%\item {\bf GTA - Computer Vision:} Held weekly office hours and grading for computer vision course. 
%\end{rSection}

% Awards & Achievements

% \begin{rSection}{Awards \& Achievements} \itemsep -3pt \vspace{-3mm}
% \item {\bf Qualifier} for the 2018 and 2015 American Invitational Mathematics Examination (AIME)
% \item {\bf Semifinalist (Top 500 in the nation)} for the 2017 and 2016 USA Biology Olympiad (USABO)
% \end{rSection}

\end{document}

