%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS

\documentclass{template} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry}
\usepackage{fontawesome} % Document margins
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Akhil Goel}
%\address{7700 Falstaff Rd, McLean, VA 22102}
\address{\href{mailto:akhil.goel.2000@gmail.com}{akhil.goel.2000@gmail.com } \\ \space \faPhone \space {(571)\:353-9527} \\ \space \faGithub \space \href{https://agaction.github.io}{agaction }}

\begin{document}

% EDUCATION SECTION

\begin{rSection}{Education}
{\bf Georgia Institute of Technology, Atlanta, GA} \hfill {\em Aug 2018 - Aug 2023}
\\ {\em M.S. in Computer Science - Machine Learning} \hfill  GPA: 3.5/4.0
\vspace{0.1cm}
\\ \underline{Notable Coursework:} Machine Learning (ML), Natural Language Processing (NLP), Interactive Robot Learning (Reinforcement Learning), Convex Optimization, High Performance Parallel Computing (HPC)

{\em B.S. in Mathematics \& Computer Science | College of Science Dean's Scholarship} \hfill  GPA: 3.67/4.0
\vspace{0.1cm}
\\ \underline{Notable Coursework:} Data Structures, Algorithms, OOP, Deep Learning, Computer Vision, Perception, AI, Computer Architecture, Systems, Databases, Networking, Linear Algebra, Probability, Statistics, Analysis
\vspace{0.20cm}
\\ {\bf Thomas Jefferson High School for Science and Technology (TJHSST)} \hfill {\em Aug 2014 - May 2018}
\end{rSection}

% WORK EXPERIENCE

\begin{rSection}{Work Experience}

\begin{rSubsection}{Google}{May 2022 - August 2022}{Software Engineering Intern}{Mountain View, CA}
\item Designed and implemented low-latency subscription free-trial fraud detection system for Google Play Store.
\item Analyzed revenue impact of abuse checks and created user experiments to enable ramp-up of abuse verdicts.
\end{rSubsection}

\begin{rSubsection}{Meta (Facebook AI Applied Research)}{May 2021 - August 2021}{Software Engineering Intern}{Menlo Park, CA}
\item Developed influential instance model interpretability algorithms for \href{https://captum.ai/}{Captum,} an open-source PyTorch library.
\item Implemented novel algorithms from recent \href{https://arxiv.org/pdf/2002.08484.pdf}{research publications} and created \href{https://captum.ai/tutorials/TracInCP_Tutorial}{tutorials} for influence methods.
\item Designed rigorous testing frameworks and applied algorithms to large Facebook AI Multimodal models.
\end{rSubsection}

\begin{rSubsection}{Varian Medical Systems}{May 2020 - August 2020}{Software Engineering Intern}{Atlanta, GA}
\item Built automized data preprocessing pipeline and deep volumetric segmentation models for tumor identification. 
\end{rSubsection}

\begin{rSubsection}{MIT Lincoln Laboratory}{June 2019 - May 2020}{Summer Research Intern \& Student Technical Researcher}{Lexington, MA}
\item Developed algorithm for novel brain imaging method using Monte Carlo techniques. Co-Authored \href{https://bit.ly/AGpaper1}{publication.}
\item$1^{\text{st}}$ Place Team prize for proposal on automatic American Sign Language translation. Received funding.
\end{rSubsection}

\end{rSection}
\vspace{-2mm}

%Projects

\begin{rSection}{Research}
{\bf Visually Grounded PointGoal Navigation at CVMLP Lab} \hfill {\em August 2021 - May 2022} \smallskip
\\Developing visual saliency methods for deep RL agent point-goal navigation in dynamic home environments. \vspace{3mm} \\
{\bf Autonomous Robot Navigation at Georgia Tech IVALab} \hfill {\em Jan 2019 - May 2020} \smallskip
\\Integrating reinforcement learning algorithms with traditional local planning and controls for robotics.
\end{rSection}

%TECHNICAL STRENGTHS

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & \hspace{-0.75cm} Python, C/C++, Java, CUDA, Bash, SQL, Solidity \\[2pt]
Technologies \& Tools & \hspace{-0.75cm} PyTorch, TensorFlow, Pandas, OpenMP, MPI, Git, Docker, AWS, Qiskit \\[2pt]
\end{tabular}

\end{rSection}

% Leadership & Extra Curricular

\begin{rSection}{Leadership \& Extracurricular} \itemsep -3pt \vspace{-3mm}
\item {\bf External Operations - The Agency:} President for AI/ML research club at Georgia Tech.
\item {\bf Graduate TA - Computer Vision:} Led keypoint matching project (SIFT), taught students in office hours. 
\end{rSection}

\end{document}

